Tables

### 2019-04-23 code/tables.rmd
Minor addition to note on table 1

rooted_relabilities %>% knitr::kable("latex", booktabs = T, col.names = c("", "$\\rho_{xy}$ = 0", "$\\rho_{xy}$ = .3", "$\\rho_{xy}$ = .5"), escape = FALSE, digits = 2) %>% 
  kable_styling(position = "left") %>% 
  footnote(threeparttable = TRUE, escape = FALSE,
           general = "Values in cells are observed effect sizes arising from the true effect size $\\\\rho_{xy}$ and measurement reliabilites $\\\\sqrt{R_{xx'}}\\\\times\\\\sqrt{R_{yy'}}$. Code to reproduce table: osf.io/kf6pt/") %>% 
  row_spec(3, hline_after = T)

>>>>

rooted_relabilities %>% knitr::kable("latex", booktabs = T, col.names = c("", "$\\rho_{xy}$ = 0", "$\\rho_{xy}$ = .3", "$\\rho_{xy}$ = .5"), escape = FALSE, digits = 2) %>% 
  kable_styling(position = "left") %>% 
  footnote(threeparttable = TRUE, escape = FALSE,
           general = "Values in cells are observed effect sizes arising from the true effect size $\\\\rho_{xy}$ and measurement reliabilites $\\\\sqrt{R_{xx'}}\\\\times\\\\sqrt{R_{yy'}}$ when sample size is infinite. Increasing differences between observed effect sizes in the columns illustrate the association between effect size, reliability of measurement and heterogeneity.  Code to reproduce table: osf.io/kf6pt/") %>% 
  row_spec(3, hline_after = T)
